---
title: "2016 In Review"
author: "Kristin Rollins"
date: "12/26/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(orfwx)
library(magrittr)
library(dplyr)
wxYear <- combineDataFrames(airportData, updatedData()) %>% 
  computeExtraDateVariables() %>% 
  filter(Year == 2016) %>%
  removeExtraDateVariables()
```

## Daily High Temperature

These are the ten **hottest** days of 2016, by daily high temperature.

```{r echo = FALSE}
wxYear %<>% mutate(Rank = as.integer(min_rank(-MaxTemperature)))
knitr::kable(
  top_n(wxYear, 10, MaxTemperature) %>%
    select(Rank, Date, MaxTemperature) %>%
    arrange(desc(MaxTemperature), desc(Date))
  )
```

These are the ten **coldest** days of 2016 (by daily high temperature)

```{r echo = FALSE}
wxYear %<>% mutate(Rank = as.integer(min_rank(MaxTemperature)))
knitr::kable(
  top_n(wxYear, -10, MaxTemperature) %>%
    select(Rank, Date, MaxTemperature) %>%
    arrange(MaxTemperature, desc(Date))
  )
```

## Daily Low Temperature

These are the ten **coldest** days of 2016, by daily low temperature.

```{r echo = FALSE}
wxYear %<>% mutate(Rank = as.integer(min_rank(MinTemperature)))
knitr::kable(
  top_n(wxYear, -10, MinTemperature) %>%
    select(Rank, Date, MinTemperature) %>%
    arrange(MinTemperature, desc(Date))
  )
```

These are the ten **hottest** days of 2016 (by daily low temperature).

```{r echo = FALSE}
wxYear %<>% mutate(Rank = as.integer(min_rank(-MinTemperature)))
knitr::kable(
  top_n(wxYear, 10, MinTemperature) %>%
    select(Rank, Date, MinTemperature) %>%
    arrange(desc(MinTemperature), desc(Date))
  )
```

## Temperature Spread

These are the ten days with the greatest spread between low and high temperatures.

```{r echo = FALSE}
wxYear %<>% computeTemperatureSpread() %>% 
  mutate(Rank = as.integer(min_rank(-TemperatureSpread)))
knitr::kable(
  top_n(wxYear, 10, TemperatureSpread) %>%
    select(Rank, Date, TemperatureSpread, MaxTemperature, MinTemperature) %>%
    arrange(desc(TemperatureSpread), desc(Date))
  )
```

These are the ten days with the smallest spread between low and high temperatures.

```{r echo = FALSE}
wxYear %<>% mutate(Rank = as.integer(min_rank(TemperatureSpread)))
knitr::kable(
  top_n(wxYear, -10, TemperatureSpread) %>%
    select(Rank, Date, TemperatureSpread, MaxTemperature, MinTemperature) %>%
    arrange(TemperatureSpread, desc(Date))
  )
```

## Precipitation

These are the ten days with the greatest precipitation.

```{r echo = FALSE, warning = FALSE}
wxYear %<>% tidyr::drop_na(CsvPrecipitation, CsvSnowfall) %>%
  convertCsvToNumericAndLogical() %>%
  mutate(Rank = as.integer(min_rank(-PrecipitationInches)))
knitr::kable(
  top_n(wxYear, 10, PrecipitationInches) %>%
    select(Rank, Date, PrecipitationInches) %>%
    arrange(desc(PrecipitationInches), desc(Date))
  )
```

## Snowfall

These are the days with snowfall (in inches, `T` is trace snowfall).

```{r echo = FALSE, warning = FALSE}
wxYear %<>% tidyr::drop_na(CsvPrecipitation, CsvSnowfall) %>%
  convertCsvToNumericAndLogical() %>%
  mutate(Rank = as.integer(min_rank(-SnowfallInches)))
knitr::kable(
  top_n(wxYear %>% filter(WithSnowfall == TRUE), 10, SnowfallInches) %>%
    select(Rank, Date, SnowfallInches, CsvSnowfall) %>%
    arrange(desc(SnowfallInches), desc(Date)) %>%
    mutate(Snowfall = CsvSnowfall) %>%
    select(-SnowfallInches, -CsvSnowfall)
  )
```
