---
title: "2016 In Review"
author: "Kristin Rollins"
date: "12/28/2016"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(orfwx)
library(magrittr)
library(dplyr)
wxYear <- combineDataFrames(airportData, updatedData()) %>% 
  computeExtraDateVariables() %>% 
  filter(Year == 2016) %>%
  removeExtraDateVariables()
```

## Daily High Temperature

These are the ten **hottest** days of 2016, by daily high temperature.

```{r echo = FALSE}
wxYear %<>% mutate(Rank = as.integer(min_rank(-MaxTemperature)))
knitr::kable(
  top_n(wxYear, 10, MaxTemperature) %>%
    select(Rank, Date, MaxTemperature) %>%
    arrange(desc(MaxTemperature), desc(Date))
  )
```

These are the ten **coldest** days of 2016 (by daily high temperature)

```{r echo = FALSE}
wxYear %<>% mutate(Rank = as.integer(min_rank(MaxTemperature)))
knitr::kable(
  top_n(wxYear, -10, MaxTemperature) %>%
    select(Rank, Date, MaxTemperature) %>%
    arrange(MaxTemperature, desc(Date))
  )
```

## Daily Low Temperature

These are the ten **coldest** days of 2016, by daily low temperature.

```{r echo = FALSE}
wxYear %<>% mutate(Rank = as.integer(min_rank(MinTemperature)))
knitr::kable(
  top_n(wxYear, -10, MinTemperature) %>%
    select(Rank, Date, MinTemperature) %>%
    arrange(MinTemperature, desc(Date))
  )
```

These are the ten **hottest** days of 2016 (by daily low temperature).

```{r echo = FALSE}
wxYear %<>% mutate(Rank = as.integer(min_rank(-MinTemperature)))
knitr::kable(
  top_n(wxYear, 10, MinTemperature) %>%
    select(Rank, Date, MinTemperature) %>%
    arrange(desc(MinTemperature), desc(Date))
  )
```

## Temperature Spread

These are the ten days with the greatest spread between low and high temperatures.

```{r echo = FALSE}
wxYear %<>% computeTemperatureSpread() %>% 
  mutate(Rank = as.integer(min_rank(-TemperatureSpread)))
knitr::kable(
  top_n(wxYear, 10, TemperatureSpread) %>%
    select(Rank, Date, TemperatureSpread, MaxTemperature, MinTemperature) %>%
    arrange(desc(TemperatureSpread), desc(Date))
  )
```

These are the ten days with the smallest spread between low and high temperatures.

```{r echo = FALSE}
wxYear %<>% mutate(Rank = as.integer(min_rank(TemperatureSpread)))
knitr::kable(
  top_n(wxYear, -10, TemperatureSpread) %>%
    select(Rank, Date, TemperatureSpread, MaxTemperature, MinTemperature) %>%
    arrange(TemperatureSpread, desc(Date))
  )
```

## Precipitation

These are the ten days with the greatest precipitation.

```{r echo = FALSE, warning = FALSE}
wxYear %<>% tidyr::drop_na(CsvPrecipitation, CsvSnowfall) %>%
  convertCsvToNumericAndLogical() %>%
  mutate(Rank = as.integer(min_rank(-PrecipitationInches)))
knitr::kable(
  top_n(wxYear, 10, PrecipitationInches) %>%
    select(Rank, Date, PrecipitationInches) %>%
    arrange(desc(PrecipitationInches), desc(Date))
  )
```

## Snowfall

These are the days with snowfall (in inches, `T` is trace snowfall).

```{r echo = FALSE, warning = FALSE}
wxYear %<>% tidyr::drop_na(CsvPrecipitation, CsvSnowfall) %>%
  convertCsvToNumericAndLogical() %>%
  mutate(Rank = as.integer(min_rank(-SnowfallInches)))
knitr::kable(
  top_n(wxYear %>% filter(WithSnowfall == TRUE), 10, SnowfallInches) %>%
    select(Rank, Date, SnowfallInches, CsvSnowfall) %>%
    arrange(desc(SnowfallInches), desc(Date)) %>%
    mutate(Snowfall = CsvSnowfall) %>%
    select(-SnowfallInches, -CsvSnowfall)
  )
```

## Counts of temperature extremes
```{r echo = FALSE}
wxYear <- filter(computeExtraDateVariables(combineDataFrames(bothStations, 
                                                             updatedData())), 
                 Year == 2016)
```

### High temperatures

Days with highs greater than or equal to...

| High temperature >= | Frequency (in days) |
|------:|-----:|
| 100 | `r as.integer(count(filter(wxYear, MaxTemperature >= 100)))` |
| 95 | `r as.integer(count(filter(wxYear, MaxTemperature >= 95)))` | |
| 90 | `r as.integer(count(filter(wxYear, MaxTemperature >= 90)))` |
| 85 | `r as.integer(count(filter(wxYear, MaxTemperature >= 85)))` |
| 80 | `r as.integer(count(filter(wxYear, MaxTemperature >= 80)))` |
| 75 | `r as.integer(count(filter(wxYear, MaxTemperature >= 75)))` |
| 70 | `r as.integer(count(filter(wxYear, MaxTemperature >= 70)))` |

Days with highs less than or equal to...

| High temperature <= | Frequency (in days) |
|------:|-----:|
| 75 | `r as.integer(count(filter(wxYear, MaxTemperature <= 75)))` |
| 70 | `r as.integer(count(filter(wxYear, MaxTemperature <= 70)))` |
| 65 | `r as.integer(count(filter(wxYear, MaxTemperature <= 65)))` |
| 60 | `r as.integer(count(filter(wxYear, MaxTemperature <= 60)))` |
| 55 | `r as.integer(count(filter(wxYear, MaxTemperature <= 55)))` |
| 50 | `r as.integer(count(filter(wxYear, MaxTemperature <= 50)))` |
| 45 | `r as.integer(count(filter(wxYear, MaxTemperature <= 45)))` |
| 40 | `r as.integer(count(filter(wxYear, MaxTemperature <= 40)))` |
| 35 | `r as.integer(count(filter(wxYear, MaxTemperature <= 35)))` |
| 32 | `r as.integer(count(filter(wxYear, MaxTemperature <= 32)))` |
| 30 | `r as.integer(count(filter(wxYear, MaxTemperature <= 30)))` |
| 25 | `r as.integer(count(filter(wxYear, MaxTemperature <= 25)))` |
| 20 | `r as.integer(count(filter(wxYear, MaxTemperature <= 20)))` |

### Low temperatures

Days with lows greater than or equal to...

| Low temperature >= | Frequency (in days) |
|------:|-----:|
| 85 | `r as.integer(count(filter(wxYear, MinTemperature >= 85)))` |
| 80 | `r as.integer(count(filter(wxYear, MinTemperature >= 80)))` |
| 75 | `r as.integer(count(filter(wxYear, MinTemperature >= 75)))` |
| 70 | `r as.integer(count(filter(wxYear, MinTemperature >= 70)))` |
| 65 | `r as.integer(count(filter(wxYear, MinTemperature >= 65)))` |
| 60 | `r as.integer(count(filter(wxYear, MinTemperature >= 60)))` |
| 55 | `r as.integer(count(filter(wxYear, MinTemperature >= 55)))` |
| 50 | `r as.integer(count(filter(wxYear, MinTemperature >= 50)))` |

Days with lows less than or equal to...

| Low temperature >= | Frequency (in days) |
|------:|-----:|
| 55 | `r as.integer(count(filter(wxYear, MinTemperature <= 55)))` |
| 50 | `r as.integer(count(filter(wxYear, MinTemperature <= 50)))` |
| 45 | `r as.integer(count(filter(wxYear, MinTemperature <= 45)))` |
| 40 | `r as.integer(count(filter(wxYear, MinTemperature <= 40)))` |
| 35 | `r as.integer(count(filter(wxYear, MinTemperature <= 35)))` |
| 32 | `r as.integer(count(filter(wxYear, MinTemperature <= 32)))` |
| 30 | `r as.integer(count(filter(wxYear, MinTemperature <= 30)))` |
| 25 | `r as.integer(count(filter(wxYear, MinTemperature <= 25)))` |
| 20 | `r as.integer(count(filter(wxYear, MinTemperature <= 20)))` |
| 15 | `r as.integer(count(filter(wxYear, MinTemperature <= 15)))` |

## Precipitation

```{r echo = FALSE, warning = FALSE}
wxYearPrecip <- select(convertCsvToNumericAndLogical(wxYear), 
                       Date, 
                       PrecipitationInches, 
                       WithPrecipitation, 
                       CsvPrecipitation)
daysWithPrecipitation <- filter(wxYearPrecip, WithPrecipitation == TRUE) %>% 
  count()
daysWithTrace <- filter(wxYearPrecip, CsvPrecipitation == "T") %>% count()
daysWithMoreThan <- function(dwmtInches) {
  dwmtCount <- filter(wxYearPrecip, PrecipitationInches >= dwmtInches) %>%
    count()
  return(dwmtCount)
}
```

There were **`r daysWithPrecipitation`** days with precipitation:

| Precipitation | Frequency (in days) |
|------:|-----:|
| Trace | `r daysWithTrace` |
| Measurable (>= 0.01 inches) | `r daysWithMoreThan(0.01)` |
| >= 0.02 inches | `r daysWithMoreThan(0.02)` |
| >= 0.03 inches | `r daysWithMoreThan(0.03)` |
| >= 0.04 inches | `r daysWithMoreThan(0.04)` |
| >= 0.05 inches | `r daysWithMoreThan(0.05)` |
| >= 0.1 inches | `r daysWithMoreThan(0.1)` |
| >= 0.2 inches | `r daysWithMoreThan(0.2)` |
| >= 0.25 inches | `r daysWithMoreThan(0.25)` |
| >= 0.5 inches | `r daysWithMoreThan(0.5)` |
| >= 0.75 inches | `r daysWithMoreThan(0.75)` |
| >= 1 inch | `r daysWithMoreThan(1)` |
| >= 1.5 inches | `r daysWithMoreThan(1.5)` |
| >= 2 inches | `r daysWithMoreThan(2)` |
| >= 3 inches | `r daysWithMoreThan(3)` |
| >= 4 inches | `r daysWithMoreThan(4)` |
| >= 5 inches | `r daysWithMoreThan(5)` |
| >= 6 inches | `r daysWithMoreThan(6)` |
| >= 7 inches | `r daysWithMoreThan(7)` |
| >= 8 inches | `r daysWithMoreThan(8)` |

## Snowfall

```{r echo = FALSE, warning = FALSE}
wxYearSnow <- select(convertCsvToNumericAndLogical(wxYear), 
                       Date, 
                       SnowfallInches, 
                       WithSnowfall, 
                       CsvSnowfall)
daysWithSnowfall <- filter(wxYearSnow, WithSnowfall == TRUE) %>% count()
daysWithTrace <- filter(wxYearSnow, CsvSnowfall == "T") %>% count()
daysWithMoreThan <- function(dwmtInches) {
  dwmtCount <- filter(wxYearSnow, SnowfallInches >= dwmtInches) %>% count()
  return(dwmtCount)
}
```

There were **`r daysWithSnowfall`** days with snowfall:

| Snowfall | Frequency (in days) |
|------:|-----:|
| Trace | `r daysWithTrace` |
| Measurable (>= 0.1 inches) | `r daysWithMoreThan(0.1)` |
| >= 0.2 inches | `r daysWithMoreThan(0.2)` |
| >= 0.3 inches | `r daysWithMoreThan(0.3)` |
| >= 0.4 inches | `r daysWithMoreThan(0.4)` |
| >= 0.5 inches | `r daysWithMoreThan(0.5)` |
| >= 1 inch | `r daysWithMoreThan(1)` |
| >= 1.5 inches | `r daysWithMoreThan(1.5)` |
