---
title: "2016 In Review"
author: "Kristin Rollins"
date: "12/26/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(orfwx)
library(magrittr)
library(dplyr)
wxYear <- combineDataFrames(airportData, updatedData()) %>% 
  computeExtraDateVariables() %>% 
  filter(Year == 2016) %>%
  removeExtraDateVariables()
```

## MaxTemperature

These are the ten hottest days of 2016.

```{r}
wxYear %<>% mutate(Rank = as.integer(rank(-MaxTemperature)))
knitr::kable(
  top_n(wxYear, 10, MaxTemperature) %>%
    select(Rank, Date, MaxTemperature) %>%
    arrange(desc(MaxTemperature), desc(Date))
  )
```

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
