---
title: "@ORF_Weather Daily Report"
output: html_notebook
---

```{r}
library(orfwx)
library(dplyr, quietly = TRUE, warn.conflicts = FALSE)
yesterWx <- orfwx::allData() %>%
  dplyr::filter(Date == orfwx::yesterdate())
```

This report is updated as of the end of 
**`r format(orfwx::yesterdate(), "%A, %b %e, %Y")`**

## Tweet-sized summary

Weather summary for `r format(orfwx::yesterdate(), "%A, %B %e")` at Norfolk, VA
airport

High: `r yesterWx[["MaxTemperature"]]`째    
Low: `r yesterWx[["MinTemperature"]]`째    
`r if(yesterWx[["CsvPrecipitation"]] == "T") {
"Precipitation: Trace"
} else if(yesterWx[["CsvPrecipitation"]] == "0.00") {
""
} else {
paste0("Precipitation: ", yesterWx[["CsvPrecipitation"]], '"')
}`

## High temperature

Yesterday had a high temperature of **`r yesterWx[["MaxTemperature"]]`**째F

```{r}
orfwx::plotMaxTempOverHistory()
```

### Extremes

We have two plots with the extremes recorded on that date.

```{r}
orfwx::plotCoolestMaxTempOverHistory()
orfwx::plotWarmestMaxTempOverHistory()
```

## Low temperature

Yesterday had a high temperature of **`r yesterWx[["MinTemperature"]]`**째F

```{r}
orfwx::plotMinTempOverHistory()
```

### Extremes

We have two plots with the extremes recorded on that date.

```{r}
orfwx::plotCoolestMinTempOverHistory()
orfwx::plotWarmestMinTempOverHistory()
```
