---
title: "@ORF_Weather Daily Report"
output: html_notebook
---

```{r}
library(orfwx)
library(dplyr, quietly = TRUE, warn.conflicts = FALSE)
yesterWx <- orfwx::allData() %>%
  dplyr::filter(Date == orfwx::yesterdate())
```

This report is updated as of the end of 
**`r format(orfwx::yesterdate(), "%A, %b %e, %Y")`**

## Tweet-sized summary

Weather summary for `r format(orfwx::yesterdate(), "%A, %B %e")` at Norfolk, VA
airport

High: `r yesterWx[["MaxTemperature"]]`째    
Low: `r yesterWx[["MinTemperature"]]`째    
`r if(is.na(yesterWx[["CsvPrecipitation"]]) | 
        yesterWx[["CsvPrecipitation"]] == "0.00") {
""
} else if(yesterWx[["CsvPrecipitation"]] == "T") {
"Precipitation: Trace"
} else {
paste0("Precipitation: ", yesterWx[["CsvPrecipitation"]], '"')
}`    
`r if(is.na(yesterWx[["CsvSnowfall"]]) | yesterWx[["CsvSnowfall"]] == "0.0") {
""
} else if(yesterWx[["CsvSnowfall"]] == "T") {
"Snowfall: Trace"
} else {
paste0("Snowfall: ", yesterWx[["CsvSnowfall"]], '"')
}`

## High temperature

Yesterday had a high temperature of **`r yesterWx[["MaxTemperature"]]`**째F

```{r}
orfwx::plotMaxTempOverHistory()
```

### Extremes

We have two plots with the extremes recorded on that date.

```{r}
orfwx::plotCoolestMaxTempOverHistory()
orfwx::plotWarmestMaxTempOverHistory()
```

## Low temperature

Yesterday had a low temperature of **`r yesterWx[["MinTemperature"]]`**째F

```{r}
orfwx::plotMinTempOverHistory()
```

### Extremes

We have two plots with the extremes recorded on that date.

```{r}
orfwx::plotCoolestMinTempOverHistory()
orfwx::plotWarmestMinTempOverHistory()
```

## Precipitation

`r if(is.na(yesterWx[["CsvPrecipitation"]])) {
"Yesterday's precipitation observation is missing."
} else if(yesterWx[["CsvPrecipitation"]] == "T") {
"Yesterday had trace precipitation recorded."
} else if(yesterWx[["CsvPrecipitation"]] == "0.00") {
"Yesterday had no precipitation recorded."
} else {
paste0("Yesterday had ", 
       yesterWx[["CsvPrecipitation"]], 
       '" of precipitation recorded.')
}`

```{r}
suppressWarnings(orfwx::plotPrecipitationOverHistory())
```

### Month and year in progress

```{r}
suppressWarnings(orfwx::plotMTDPrecipitation())
suppressWarnings(orfwx::plotYTDPrecipitation())
```

## Snowfall

`r if(is.na(yesterWx[["CsvSnowfall"]])) {
"Yesterday's snowfall observation is missing."
} else if(yesterWx[["CsvSnowfall"]] == "T") {
"Yesterday had trace snowfall recorded."
} else if(yesterWx[["CsvSnowfall"]] == "0.0") {
"Yesterday had no snowfall recorded."
} else {
paste0("Yesterday had ", yesterWx[["CsvSnowfall"]], '" of snowfall recorded.')
}`
